The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-29 document/ms.tex
refs
some words about vetting and candidate selection

@@

@@

\subsection{Initial candidate events}

@@

To generate this list, we apply a standard ``box least squares'' (BLS;
\dfmtodo{CITE}) method with a single (non-periodic) box.
First, we filter the PDC (\dfmtodo{CITE}) light curves using a running
windowed median with a half-width of \dfmtodo{how many} to remove stellar
variability.
We then compute the signal-to-noise of the depth of a 0.6~day long transit on
a grid of times spanning the full \kepler\ baseline.
We only need to use a single transit duration because the following steps in
this procedure are only sensitive to transits with very high signal-to-noise
so, in practice, the results of this step are insensitive to the specific
choice of duration.

As previously mentioned, the following steps will only detect high
signal-to-noise transits.
To avoid edge effects, we apodize this detection scalar near any large gaps in
the time series using a logistic function with width equal to one transit
duration.
Finally, we estimate the noise in the time series using a robust running
windowed variance estimate of the detection scalar and accepting peaks more
than 25-times this noise as candidates.

\subsection{Light curve-level vetting}

@@

For up to three candidate transit times per light curve, we select a
contiguous chunk of PDC light curve approximately centered on the proposed
transit with no more than 500 cadences \dfmtodo{check me} and compute the BIC
of each model for this data set.
We will define the BIC for a model $k$ in the set of $K$ models is given by
\begin{eqnarray}
\mathrm{BIC}_k &=& \ln \mathcal{L}^* - \frac{J}{2}\,\log N
\end{eqnarray}
where the likelihood function $\mathcal{L}$ is evaluated at its maximum, $J$
is the number of free parameters in the model, and $N$ is the number of
data points in the data set.

@@

The models are:
\begin{itemize}
{\item a limb-darkened, exposure time integrated transit light curve,}
{\item a pure Gaussian Process model to capture stellar variability,}
{\item a single outlier,}
{\item an step function, and}
{\item a box.}
\end{itemize}

@@

\begin{figure*}~\\
\begin{center}
\includegraphics{figures/full_sample.pdf}
\end{center}
\caption{%
Blah.
\dfmfiglabel{full-sample}}~\\
\end{figure*}

>>>>

\usepackage{microtype}

@@

EB catalog: \citep{Kirk:2016}

Microlensing OR: \citep{Shvartzvald:2016}

@@

\subsection{Step 1 -- Initial candidate events}

@@

To generate this list, we use a method much like the standard ``box least
squares'' (BLS; \dfmtodo{CITE}) procedure with a single (non-periodic) box.
First, we filter the PDC (\dfmtodo{CITE}) light curves using a running
windowed median with a half-width of \dfmtodo{how many} to remove stellar
variability.
We then compute the signal-to-noise of the depth of a 0.6~day long
transit on a grid of times spanning the full baseline of observations.

In detail, at each proposal time $t_0$, we hypothesize a box-shaped transit
with duration $\tau$
\begin{eqnarray}
m(t) &=& \left\{\begin{array}{ll}
    \mu, & \mbox{\,if $|t - t_0| < \tau/2$} \\
    \mu - \delta, & \mbox{\,otherwise}
\end{array}\right. \quad.
\end{eqnarray}
Assuming that the uncertainties on the observed fluxes $f(t)$ are Gaussian
with known variance ${\sigma_f}^2$, the likelihood function for the mean flux
$\mu$ and transit depth $\delta$ can be analytically computed to be a
two-dimensional Gaussian with mean and covariance given by linear
least-squares.
This likelihood function provides a natural scalar objective: the
signal-to-noise of the measured depth $\delta / \sigma_\delta$ computed a
function of time.
In principle this scalar is also a function of duration but we only use a
single transit duration because the following steps in this procedure are only
sensitive to transits with very high signal-to-noise.
In practice, the final results are insensitive to the specific choice of
duration.

To avoid edge effects, we apodize this detection scalar near any large gaps in
the time series using a logistic function with width equal to one transit
duration.
Finally, we estimate the background noise level in the detection scalar time
series using a robust running windowed variance estimate of the detection
scalar and accepting peaks more than 25-times this noise as candidates.

For the \kepler\ light curves, this procedure yields at least one candidate
event in about 10~percent of targets and the three highest signal-to-noise
events are investigated in the following step.

\subsection{Step 2 -- Light curve vetting}

@@

For up to three candidate transit times per light curve, we select a
contiguous chunk of PDC light curve approximately centered on the proposed
transit with no more than 500 cadences \dfmtodo{check me} and compute the BIC
of each model for this data set.
The BIC for a model $k$ in the set of $K$ models is given by
\begin{eqnarray}
\mathrm{BIC}_k &=& \ln \mathcal{L}^* - \frac{J}{2}\,\log N
\end{eqnarray}
where the likelihood function $\mathcal{L}$ is evaluated at its maximum, $J$
is the number of free parameters in the model, and $N$ is the number of
data points in the data set.

@@

We consider the following mean models and this list provides a qualitative
justification for each model:
\begin{itemize}
{\item a limb-darkened, exposure time integrated transit light curve,}
{\item a pure Gaussian Process model to capture stellar variability,}
{\item a single outlier to account for a bad data point,}
{\item a step function to describe sudden pixel sensitivity dropouts (SPSDs;
\dfmtodo{CITE}), and}
{\item a box to catch signals that are well fit by the search scalar but
insufficiently transit-like to be convincing.}
\end{itemize}
The functional forms of these models are given in Appendix \dfmtodo{SOME APP}.

This method of automated vetting is clearly limited by the specific models
selected in this step.
We find that these are sufficient for the targets discussed below but other
target lists might require additional models to be included for robust
selection.

@@

\begin{figure*}[p]~\\
\begin{center}
\include{lcfig}
\end{center}
\caption{%
\dfmfiglabel{lightcurves}}
\end{figure*}

\begin{figure*}~\\
\begin{center}
\includegraphics{figures/full_sample_plus_cands.pdf}
\end{center}
\caption{%
Blah.
\dfmfiglabel{full-sample}}~\\
\end{figure*}

\begin{deluxetable}{cccccl}
\tabletypesize{\footnotesize}
\tablecaption{caption\label{tab:table}}
\include{paramtab}
% \tablenotetext{a}{Adjusted for inflation}
% \tablenotetext{b}{Accounts for the change from page charges to digital quanta in April, 2011}
% \tablecomments{Note that {\tt \string \colnumbers} does not work with the
% vertical line alignment token. If you want vertical lines in the headers you
% can not use this command at this time.}
\end{deluxetable}
